\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
formative procedure rewriting

\subsection{Procedure}
{\color {blue}
When a participant entered the room, researchers informed them of purpose of the study, data collected, and associated risks. 
A researcher informed the participant of the simulated censorship environment and
instruct them to visit sample blocked and unblocked websites
in a standard browser (Appendix~\ref{qualitative-script}). 
This shows participants what a blocked site looks like in a browser. 
Then, the participant was asked to complete a worksheet that gives information
on their censorship environment and instructed them
to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
The worksheet informed the participant that the network is censored,
but did not give details of what services and websites are specifically blocked.
Participants were able to visit the unblocked website using any familiar browser,
but had to configure Tor Browser in order to visit the blocked website.

For the blocked website, we used the main page of Wikipedia,
and for the unblocked site we used the CNN homepage.
We chose these two sites because of their likely familiarity to web users;
our goal was to evaluate the user interface, not to test users with a browsing task.
After instructions, the researchers stepped out of the room.There was no interaction
between the participant and researcher for the rest of the session.
Researchers watched a live video of each participant's screen from another room
and saved the videos for review.

Participants had an average of 45 minutes to complete their worksheet. 
After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked questions asking about their general experience, 
interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
We followed up with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time. 
}

>>>>

\subsection{Procedure}
Before the experiment began, each participant was verbally informed of the purpose of the 
study, what data was collected, and any associated risks. If they wished to participate,
they were informed again in writing and consented by signing the document. To be thorough, 
we clarified verbally that they could stop at any time during the experiment with no negative consequences.

The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}). This purpose of this introduction was to ensure that the main task
was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
We instructed them to visit a blocked and unblocked website
in a non-Tor browser to clarify that the Internet was functioning as expected. 
We then told them to use Tor Browser to visit a censored site and pointed out 
the respective shortcut on their desktop.

We then asked them to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
required answers from one blocked website (Wikipedia) and one non-blocked website (CNN).
The worksheet did not specify which website was censored. 
We chose these websites because they are popular websites and that their likely familiarity 
would make the task seem less intimidating.

Participants were given 45 minutes to complete their worksheet. 
After instructions, the researchers left and watched a live feed of the participants' screen in another room to minimize interactions.

After participants completed the browsing tasks (or ran out of time),
we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses. We then followed up with participant-specific questions to verify any hypotheses we had from observation (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.
